### 2019-10-11 2019 Journal/binaryFDT.tex
Add files via upload

\section{Finding a feasible solution}\label{domTOIP}
Consider a formulation instance $I=(A,G,b)$. Define sets $S(I)$ and $P(I)$ as in (\ref{S}) and (\ref{P}), respectively. Assume $S(I),P(I)\subseteq [0,1]^n\times \mathbb{R}^p$. For simplicity in the notation we denote $P(I),S(I),$ and $g(I)$ with $P$, $S$, and $g$ for this section and the next section. Also, for both sections we assume $t=|\spp(x)|$. Without loss of generality we can assume $x_i = 0$ for $i=t+1,\ldots,n$. For polyhedron $L$ in $\mathbb{R}^{n\times p}$ let $\dom(L)= \{(x,y)\in \mathbb{R}^n\times \mathbb{R}^p: x\geq x' \text{ for some } (x',y')\in L\}$, and we call $\dom(L)$ the dominant of $L$.

In this section we prove Theorem \ref{domtoIP}. In fact, we prove a stronger result. 
\begin{lemma}\label{domlemma}
	Given $(x,y)\in \dom(P)$ where $x\in \mathbb{Z}^n$, there is an algorithm (the DomToIP algorithm) that finds $(\bar{x},\bar{y})\in S$ in polynomial time, such that $\bar{x}\leq x$.\end{lemma}

We prove Lemma \ref{domlemma} by introducing an algorithm that ``fixes" the variables iteratively, starting from $x_1$ and ending at $x_t$. Suppose we run the algorithm for $\ell\in \{0,\ldots,t-1\}$ iterations and we have $(x^{(\ell)},y^{(\ell)})\in \dom(P)$  such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,n$. Now consider the following linear program. The variables of this linear program are the $z\in \mathbb{R}^n$ variables and $w\in \mathbb{R}^p$.

\begin{align}
	\DOMtoS(x^{(\ell)})\quad\quad& \min\quad \;z_{\ell+1}\\
	&\;\text{s.t.} \quad \;\;Az+ Gw\geq b \\
	&\;{\color{white}{\text{s.t.}} }\quad \;\; \; z_j = x^{(\ell)}_j \quad \; j =1,\ldots, \ell\\
	&\;{\color{white}{\text{s.t.}} }\quad \; \;\; z_j \leq x^{(\ell)}_j \quad \; j = \ell+1,\ldots,n\\
	&\;{\color{white}{\text{s.t.}} }\quad \; \;\; z\;\geq 0
\end{align}

@@

The above procedure suggests how to find $(x^{(\ell+1)},y^{(\ell+1)})$ from $(x^{(\ell)},y^{(\ell)})$. The DomToIP algorithm initializes with $(x^{(0)},y^{(0)})=(x,y)$ and  iteratively calls this procedure in order to obtain $(x^{(t)},y^{(t)})$.

\vspace*{10pt}
\begin{algorithm}[H]
	\KwIn{$(x,y)\in \dom(P)$, $x\in \mathbb{Z}^n$}
	\KwOut{$(x^{(t)},y^{(t)}) \in S$, $x^{(t)}\leq x$}
	$x^{(0)}\leftarrow x$\\
	\For{$\ell = 0$ \textbf{to} $t-1$}{
		$x^{(\ell+1)} \leftarrow x^{(\ell)}$\\
		$\eta \leftarrow$ optimal value of $ \DOMtoS(x^{(\ell)})$\\
		$y^{(\ell+1)}\leftarrow$ optimal solution for $w$ variables in $ \DOMtoS(x^{(\ell)})$\\
		\eIf{$\eta = 0$}{
			$x^{(\ell+1)}_{\ell+1} \leftarrow 0$\
		}{
			$x^{(\ell+1)}_{\ell+1} \leftarrow 1$
		}
	}
	\caption{The DomToIP algorithm}
	\label{domtoIPalg}
\end{algorithm}
\vspace*{10pt}
We prove that indeed $(x^{(t)},y^{(t)})\in S$. First, we need to show that in any iteration $\ell=  0,\ldots,t-1$ of DomToIP, the feasible region of $\DOMtoS(x^{\ell})$ is non-empty. We show something stronger. For $\ell=0,\ldots,t-1$ let
	\begin{align*}
	\LP^{(\ell)}&= \{(z,w)\in P\; : \; z\leq x^{(\ell)} \mbox{ and } z_j=x_j^{(\ell)} \mbox{ for } j=1,\ldots,\ell\}, \text{ and}\\
	\IP^{(\ell)}&= \{(z,w)\in \LP^{(\ell)}\; : \; z\in \{0,1\}^n\}.
	\end{align*}
	Notice that if $\LP^{(\ell)}$ is a non-empty set then $\DOMtoS(x^{(\ell)})$ is feasible. We show by induction on $\ell$ that $\LP^{(\ell)}$ and $\IP^{(\ell)}$ are not empty sets for $\ell=0,\ldots,t-1$. First notice that $\LP^{(0)}$ is clearly non-empty since by definition $(x^{(0)},y^{(0)})\in \dom(P)$, meaning there exists $(z,w)\in P$ such that $z\leq x^{(0)}$. By Theorem \ref{CV}, there exists $(\tilde{z}^i,\tilde{w}^i) \in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz$.	Thus we have $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz\leq gx^{(0)}$. So if $x^{(0)}_j=0$, then $ \sum_{i=1}^{k}\theta_i \tilde{z}_j^i =0$, which implies that $\tilde{z}^i_j=0$ for all $i=1,\ldots,k$ and $j= 1,\ldots,n$ where $x^{(0)}_j=0$. Also recall that $x^{(0)}\in \mathbb{Z}^n$.	Hence, $\tilde{z}^i\leq x^{(0)}$ for $i=1,\ldots,k$. Therefore $(\tilde{z}^i,\tilde{w}^i)\in \IP^{(0)}$ for $i=1,\ldots,k$, which implies $\IP^{(0)}\neq \emptyset$.

@@

	We consider two cases. In the first case, we have $z^*_{\ell+1}=0$. In this case we have $x^{(\ell+1)}_{\ell+1}=0$. Since $z^*\leq x^{(\ell+1)}$, we have $(z^*,w^*)\in \LP^{(\ell+1)}$. Also, $(z^*,w^*)\in P$. By Theorem \ref{CV} there exists $(\tilde{z}^i,\tilde{w}^i)\in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and  $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*$. We have $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*\leq gx^{(\ell+1)}$
	So for $j\in \{1,\ldots,n\}$ where $x^{(\ell+1)}_j=0$, we have $z^i_j=0$ for $i=1,\ldots,k$. Hence, $\tilde{z}^i\leq x^{(\ell+1)}$ for $i=1,\ldots,k$. Hence, there exists $(z,w)\in S$ such that $z\leq x^{(\ell+1)}$. We claim that $(z,w)\in \IP^{(\ell+1)}$. If $(z,w)\notin \IP^{(\ell+1)}$ we must have $1\leq j \leq \ell$ such that $z_j < x^{(\ell+1)}_{j}$, and thus $z_j = 0$ and $x^{(\ell+1)}_j=1$. Without loss of generality assume $j$ is minimum number satisfying $z_j < x^{(\ell+1)}_{j}$. Consider iteration $j$ of the DomToIP algorithm. Notice that $z\leq x^{(\ell+1)}\leq x^{({j-1})}\leq x^{(j)}$. We have $x^{(j)}_j=1$ which implies when we solved $\DOMtoS(x^{(j-1)})$ the optimal value was strictly larger than zero. However, $(z,w)$ is a feasible solution to $\DOMtoS(x^{(j-1)})$ and gives an objective value of 0. This is a contradiction, so $(z,w)\in \IP^{(\ell+1)}$.

@@

	Now consider $(x^{(t)},y^{(t)})$. Let $(z,y^{(t)})$ be the optimal solution to $\LP^{(t-1)}$. If $x^{(t)} = 0$, we have $x^{(t)} = z$, which implies that $(x^{(t)},y^{(t)})\in P$, and since $x^{(t)}\in \{0,1\}^n$ we have $(x^{(t)},y^{(t)})\in S$. If $x^{(t)} =1$, it must be the case that $z_t > 0$. By the argument above there is a point $(z',w')\in \IP^{(t-1)}$. We show that $x^{(t)} = z'$. For $j=1,\ldots,n-1$ we have $z'_j= x_j^{(t-1)}=x_j^{(t)}$. We just need to show that $z'_j = 1$. Assume $z'_j = 0$ for contradiction, then $(z',w')\in \LP^{(t-1)}$ has objective value of $0$ for $\DOMtoS(x^{(t-1)})$, this is a contradiction to $(z,w)$ being the optimal solution. This concludes the proof of Lemma \ref{domlemma}.

	Notice that Lemma \ref{domlemma} implies Theorem \ref{domtoIP}, since it is easy to obtain an integer point in $\dom(P)$: rounding up any fractional point in $P$ gives us an integral point in $\dom(P)$.

@@

Assume we are given a point $(x^*,y^*)\in P$. For instance, $(x^*,y^*)$ can be the optimal solution of minimizing a cost function $cx$ over set $P$, which provides a lower bound on $\min_{(x,y)\in S} cx$.  In this section, we prove Theorem \ref{binaryFDT} by describing the Fractional Decomposition Tree (FDT) algorithm. We also remark that if $g=1$, then the algorithm will give an exact decomposition of any feasible solution.

@@

	\begin{claim}\label{CVexists}
		We have $\gamma_0 + \gamma_1\geq \frac{1}{g}$.
	\end{claim}
	\begin{proof}
		We show that there is a feasible solution that achieves the objective value of $\frac{1}{g}$. By Theorem \ref{CV} there exists $\theta \in [0,1]^k$, with $\sum_{i=1}^{k}\theta_i = 1$ and $(\tilde{x}^i,\tilde{y}^i)\in S$ for $i=1,\ldots,k$ such that 
		$\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq gx'$.

		\begin{equation}\label{splitting}
		x'\geq \sum_{i=1}^{k}\frac{\theta_i}{g} \tilde{x}^i
		={\sum_{i\in [k]: \tilde{x}^i_\ell =0}\frac{\theta_i}{g} \tilde{x}^i}+{\sum_{i\in [k]: \tilde{x}^i_\ell =1}\frac{\theta_i}{g} \tilde{x}^i}
		\end{equation}
		For $j=0,1$, let $(x^j,y^j) = \sum_{i\in [k]:\tilde{x}^i_\ell=j} \frac{\theta_i}{g}(\tilde{x}^i,\tilde{y}^i)$. Also let $\lambda_0=\sum_{i\in [k]: \tilde{x}^i_\ell =0}\frac{\theta_i}{g}$ and $\lambda_1 = \sum_{i\in [k]: \tilde{x}^i_\ell =1}\frac{\theta_i}{g}$. Note that $\lambda_0+\lambda_1 = \frac{1}{g}$. Constraint (\ref{packing}) is satisfied by Inequality (\ref{splitting}). Also, for $j=0,1$ we have
		\begin{equation}
		Ax^j+Gy^j = \sum_{i\in[k], \tilde{x}^i_\ell = j} \frac{\theta_i}{g} (A\tilde{x}^i + G\tilde{y}^i) \geq b \sum_{i\in[k], \tilde{x}^i_\ell = j} \frac{\theta_i}{g} = b\lambda_j.
		\end{equation}
		Hence, Constraints (\ref{feasibility}) holds. Constraint (\ref{branchcoordinate}) also holds since $x^0_\ell$ is obviously $0$ and $x^1_\ell= \sum_{i\in [k]: \tilde{x}^i_\ell = 1}\frac{\theta_i}{g}= \lambda_1$. The rest of the constraints trivially hold. 
	\end{proof}
	This concludes the proof of Lemma \ref{LPClemma}.	
\end{proof}

We now show if $x'$ in the statement of Lemma \ref{LPClemma} is partially integral, we can find solutions with more integral components.
\begin{lemma}\label{round-up}
	Given $(x',y')\in \dom(P)$, such that $x'_1,\ldots,x'_{\ell-1}\in \{0,1\}$ for some $\ell\geq 1$, we can find in polynomial time vectors $(\hat{x}^0,\hat{y}^0),(\hat{x}^1,\hat{y}^1)$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that: (i) $\frac{ 1}{g}\leq \gamma_0 + \gamma_1  \leq 1$, (ii) $(\hat{x}^0,\hat{y}^0)$ and $(\hat{x}^1,\hat{y}^1)$ are in  $\dom( P)$, (iii) $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$, (iv) $ \gamma_0\hat{x}^0 +\gamma_1 \hat{x}^1 \leq
		x'$,(v) $\hat{x}^i_j\in \{0,1\}$ for $i=0,1$ and $j=1,\ldots,\ell-1$.
\end{lemma} 
\begin{proof}
	By Lemma \ref{LPClemma} we can find $(\bar{x}^0,\bar{y}^0)$, $(\bar{x}^1,\bar{y}^1)$, $\gamma_0$ and $\gamma_1$ that satisfy (i), (ii), (iii), and (iv). We define $\hat{x}^0$ and $\hat{x}^1$ as follows. For $i=0,1$, for $j=1,\ldots,\ell-1$, let $\hat{x}^i_j= \ceil{\bar{x}^i_j}$, for $j=\ell,\ldots,t$ let $\hat{x}^i_j = \bar{x}^i_j$. We now show that $(\hat{x}^0,\bar{y}^0)$, $(\hat{x}^1,\bar{y}^1)$, $\gamma_0$, and $\gamma_1$ satisfy all the conditions. Note that conditions (i), (ii), (iii), and (v) are trivially satisfied. Thus we only need to show (iv) holds. We need to show that $\gamma_0 \hat{x}^0_j+\gamma_1\hat{x}^1_j\leq gx'_j$. If $j=\ell,\ldots,t$, then this clearly holds. Hence, assume $j\leq \ell-1$. By the property of $x'$ we have $x'_j\in \{0,1\}$. If $x'_j= 0$, then by Constraint (\ref{packing}) we have $\bar{x}^0_j = \bar{x}^1_j=0$. Therefore, $\hat{x}^i_j=0$ for $i=0,1$, so (iv) holds. Otherwise if $x'_j = 1$, then we have
	$\gamma_0\hat{x}^0_j+\gamma_1\hat{x}^1_j\leq \gamma_0+\gamma_1\leq 1\leq x'_j.$ 
	Therefore (v) holds.
\end{proof}

@@

	\begin{algorithm}[H]\label{FDTFull}
		\KwIn{$P= \{(x,y)\in \mathbb{R}^{n+ p}: Ax+Gy\geq b\}$ and $S=\{(x,y)\in P: x\in \{0,1\}^n\}$ such that $g=\max_{c\in \mathbb{R}^n_+ }\frac{\min_{(x,y)\in S }cx}{\min_{(x,y)\in P}cx}$ is finite, $(x^*,y^*)\in P$}
		\KwOut{$(z^i,w^i)\in S$ and $\lambda_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\lambda_i = 1$, and $\sum_{i=1}^{k}\lambda_iz^i\leq g^kx^*$  for a $k\leq t$}
		$L^0\leftarrow [(x^*,y^*),1]$\\
		\For{$i=1$ \textbf{to} $t$}{
			$L'\leftarrow \emptyset$\\
			\For{$[(x,y),\lambda] \in L^i$}{
				Apply Lemma \ref{round-up} to obtain $[(\hat{x}^0,\hat{y}^0),\gamma_0]$ and $[(\hat{x}^1,\hat{y}^1),\gamma_1]$\\
				$L' \leftarrow L' \cup \{[(\hat{x}^0,\hat{y}^0),\lambda\gamma_0]\} \cup \{[(\hat{x}^1,\hat{y}^1),\lambda\gamma_1]\}$\\			
			}
			Apply $\prun(L')$ to obtain $L^{i+1}$. 
		}
		\For{$[(x,y),\lambda] \in L^t$}{
			Apply Algorithm \ref{domtoIPalg} to $(x,y)$ to obtain $(z,w)\in S$\\
			$F \leftarrow F \cup \{[(z,w),\lambda]\}$
		}
		\textbf{return} $F$
		\caption{Fractional Decomposition Tree Algorithm}
	\end{algorithm}

>>>>

\section{Finding a feasible solution}\label{domTOIP}
Consider a formulation instance $I=(A,G,b)$. Define sets $S(I)$ and $P(I)$ as in (\ref{S}) and (\ref{P}), respectively. Assume $S(I)\subseteq \{0,1\}^n\times \mathbb{R}^p$ and $P(I)\subseteq [0,1]^n\times \mathbb{R}^p$. For simplicity in the notation we denote $P(I),S(I),$ and $g(I)$ with $P$, $S$, and $g$ for this section and the next section. Also, for both sections we assume $t=|\spp(x)|$. Without loss of generality we can assume $x_i = 0$ for $i=t+1,\ldots,n$.

In this section we prove Theorem \ref{domtoIP}. In fact, we prove a stronger result. 
\begin{lemma}\label{domlemma}
	Given $(\tilde{x},\tilde{y})\in \dom(P)$ and $\tilde{x}\in \{0,1\}^n$, there is an algorithm (the DomToIP algorithm) that finds $(\bar{x},\bar{y})\in S$ in polynomial time, such that $\bar{x}\leq \tilde{x}$.\end{lemma}

We prove Lemma \ref{domlemma} by introducing an algorithm that ``fixes" the variables iteratively, starting from $x_1$ and ending at $x_t$. Suppose we run the algorithm for $\ell\in \{0,\ldots,t-1\}$ iterations and we have $(x^{(\ell)},y^{(\ell)})\in \dom(P)$  such that $x^{(\ell)}_i\in \{0,1\}$ for $i=1,\ldots,t$. Now consider the following linear program. The variables of this linear program are the $z\in \mathbb{R}^n$ variables and $w\in \mathbb{R}^p$.
\begin{align}
	\DOMtoS(x^{(\ell)})\quad\quad& \min\quad \;z_{\ell+1}\\
	&\;\text{s.t.} \quad \;\;Az+ Gw\geq b \\
	&\;{\color{white}{\text{s.t.}} }\quad \;\; \; z_j = x^{(\ell)}_j \quad \; j =1,\ldots, \ell\\
	&\;{\color{white}{\text{s.t.}} }\quad \; \;\; z_j \leq x^{(\ell)}_j \quad \; j = \ell+1,\ldots,n\\
	&\;{\color{white}{\text{s.t.}} }\quad \; \;\; z\;\geq 0
\end{align}

@@

The above procedure suggests how to find $(x^{(\ell+1)},y^{(\ell+1)})$ from $(x^{(\ell)},y^{(\ell)})$. The DomToIP algorithm initializes with $(x^{(0)},y^{(0)})=(\tilde{x},\tilde{y})$ and  iteratively calls this procedure in order to obtain $(x^{(t)},y^{(t)})$.

\vspace*{10pt}
\begin{algorithm}[H]
	\KwIn{$(\tilde{x},\tilde{y})\in \dom(P)$, $\tilde{x}\in \{0,1\}^n$ }
	\KwOut{$(x^{(t)},y^{(t)}) \in S$, $x^{(t)}\leq \tilde{x}$}
	$x^{(0)}\leftarrow \tilde{x}$\\
	\For{$\ell = 0$ \textbf{to} $t-1$}{
		$x^{(\ell+1)} \leftarrow x^{(\ell)}$\\
		$\eta \leftarrow$ optimal value of $ \DOMtoS(x^{(\ell)})$\\
		$y^{(\ell+1)}\leftarrow$ optimal solution for $w$ variables in $ \DOMtoS(x^{(\ell)})$\\
		\eIf{$\eta = 0$}{
			$x^{(\ell+1)}_{\ell+1} \leftarrow 0$\
		}{
			$x^{(\ell+1)}_{\ell+1} \leftarrow 1$
		}
	}
	\caption{The DomToIP algorithm}
	\label{domtoIPalg}
\end{algorithm}
\vspace*{10pt}
We prove that indeed $(x^{(t)},y^{(t)})\in S$. First, we need to show that in any iteration $\ell=  0,\ldots,t-1$ of DomToIP the $\DOMtoS(x^{(\ell)})$ is feasible. We show something stronger. For $\ell=0,\ldots,t-1$ let
	\begin{align*}
	\LP^{(\ell)}&= \{(z,w)\in P\; : \; z\leq x^{(\ell)} \mbox{ and } z_j=x_j^{(\ell)} \mbox{ for } j=1,\ldots,\ell\}, \text{ and}\\
	\IP^{(\ell)}&= \{(z,w)\in \LP^{(\ell)}\; : \; z\in \{0,1\}^n\}.
	\end{align*}
	Notice that if $\LP^{(\ell)}$ is a non-empty set then $\DOMtoS(x^{(\ell)})$ is feasible. We show by induction on $\ell$ that $\LP^{(\ell)}$ and $\IP^{(\ell)}$ are not empty sets for $\ell=0,\ldots,t-1$. First notice that $\LP^{(0)}$ is clearly feasible since by definition $(x^{(0)},y^{(0)})\in \dom(P)$, meaning there exists $(z,w)\in P$ such that $z\leq x^{(0)}$. By Theorem \ref{CV}, there exists $(\tilde{z}^i,\tilde{w}^i) \in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz$. Hence, $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz\leq gx^{(0)}$. So if $x^{(0)}_j=0$, then $ \sum_{i=1}^{k}\theta_i \tilde{z}_j^i =0$, which implies that $\tilde{z}^i_j=0$ for all $i=1,\ldots,k$ and $j= 1,\ldots,n$ where $x^{(0)}_j=0$. Hence, $\tilde{z}^i\leq x^{(0)}$ for $i=1,\ldots,k$. Therefore $(\tilde{z}^i,\tilde{w}^i)\in \IP^{(0)}$ for $i=1,\ldots,k$, which implies $\IP^{(0)}\neq \emptyset$.

@@

	We consider two cases. In the first case, we have $z^*_{\ell+1}=0$. In this case we have $x^{(\ell+1)}_{\ell+1}=0$. Since $z^*\leq x^{(\ell+1)}$, we have $(z^*,w^*)\in \LP^{(\ell+1)}$. Also, $(z^*,w^*)\in P$. By Theorem \ref{CV} there exists $(\tilde{z}^i,\tilde{w}^i)\in S$ and $\theta_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k} \theta_i = 1$ and  $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*$. We have $\sum_{i=1}^{k}\theta_i \tilde{z}^i \leq gz^*\leq gx^{(\ell+1)}$.
	So for $j\in \{1,\ldots,n\}$ where $x^{(\ell+1)}_j=0$, we have $z^i_j=0$ for $i=1,\ldots,k$. This implies $\tilde{z}^i\leq x^{(\ell+1)}$ for $i=1,\ldots,k$. Hence, there exists $(z,w)\in S$ such that $z\leq x^{(\ell+1)}$. We claim that $(z,w)\in \IP^{(\ell+1)}$. If $(z,w)\notin \IP^{(\ell+1)}$ we must have $1\leq j \leq \ell$ such that $z_j < x^{(\ell+1)}_{j}$, and thus $z_j = 0$ and $x^{(\ell+1)}_j=1$. Without loss of generality assume $j$ is minimum number satisfying $z_j < x^{(\ell+1)}_{j}$. Consider iteration $j$ of the DomToIP algorithm. Notice that $z\leq x^{(\ell+1)}\leq x^{(j)}$. We have $x^{(j)}_j=1$ which implies when we solved $\DOMtoS(x^{(j-1)})$ the optimal value was strictly larger than zero. However, $(z,w)$ is a feasible solution to $\DOMtoS(x^{(j-1)})$ and gives an objective value of 0. This is a contradiction, so $(z,w)\in \IP^{(\ell+1)}$.

@@

	Now consider $(x^{(t)},y^{(t)})$. Let $(z,y^{(t)})$ be the optimal solution to $\LP^{(t-1)}$. If $x^{(t)}_t = 0$, we have $x^{(t)} = z$, which implies that $(x^{(t)},y^{(t)})\in P$, and since $x^{(t)}\in \{0,1\}^n$ we have $(x^{(t)},y^{(t)})\in S$. If $x^{(t)}_t =1$, it must be the case that $z_t > 0$. By the argument above there is a point $(z',w')\in \IP^{(t-1)}$. We show that $x^{(t)} = z'$. For $j=1,\ldots,t-1$ we have $z'_j= x_j^{(t-1)}=x_j^{(t)}$. We just need to show that $z'_t = 1$. Assume $z'_t	 = 0$ for contradiction, then $(z',w')\in \LP^{(t-1)}$ has objective value of $0$ for $\DOMtoS(x^{(t-1)})$, this is a contradiction to $(z,w)$ being the optimal solution. This concludes the proof of Lemma \ref{domlemma}.

	Notice that Lemma \ref{domlemma} implies Theorem \ref{domtoIP}, since it is easy to obtain an integer point in $\dom(P)$: rounding up any fractional point in $P$ gives us a point in $\dom(P)$.

@@

Assume we are given a point $(x^*,y^*)\in P$. For instance, $(x^*,y^*)$ can be the optimal solution of minimizing a cost function $cx$ over set $P$, which provides a lower bound on $\min_{(x,y)\in S(I)} cx$.  In this section, we prove Theorem \ref{binaryFDT} by describing the Fractional Decomposition Tree (FDT) algorithm. We also remark that if $g_I=1$, then the algorithm will give an exact decomposition of any feasible solution.

@@

	\begin{claim}\label{CVexists}
		We have $\gamma_0 + \gamma_1\geq \frac{1}{g}$.
	\end{claim}
	\begin{proof}
		We show that there is a feasible solution that achieves the objective value of $\frac{1}{g}$. By Theorem \ref{CV} there exists $\theta \in [0,1]^k$, with $\sum_{i=1}^{k}\theta_i = 1$ and $(\tilde{x}^i,\tilde{y}^i)\in S$ for $i=1,\ldots,k$ such that 
		$\sum_{i=1}^{k}\theta_i \tilde{x}^i\leq gx'$. So

		\begin{equation}\label{splitting}
		x'\geq \sum_{i=1}^{k}\frac{\theta_i}{g} \tilde{x}^i
		={\sum_{i\in [k]: \tilde{x}^i_\ell =0}\frac{\theta_i}{g} \tilde{x}^i}+{\sum_{i\in [k]: \tilde{x}^i_\ell =1}\frac{\theta_i}{g} \tilde{x}^i}.
		\end{equation}
		For $j=0,1$, let $(x^j,y^j) = \sum_{i\in [k]:\tilde{x}^i_\ell=j} \frac{\theta_i}{g}(\tilde{x}^i,\tilde{y}^i)$. Also let $\lambda_0=\sum_{i\in [k]: \tilde{x}^i_\ell =0}\frac{\theta_i}{g}$ and $\lambda_1 = \sum_{i\in [k]: \tilde{x}^i_\ell =1}\frac{\theta_i}{g}$. Note that $\lambda_0+\lambda_1 = \frac{1}{g}$. Constraint (\ref{packing}) is satisfied by Inequality (\ref{splitting}). Also, for $j=0,1$ we have
		\begin{equation}
		Ax^j+Gy^j = \sum_{i\in[k], \tilde{x}^i_\ell = j} \frac{\theta_i}{g} (A\tilde{x}^i + G\tilde{y}^i) \geq b \sum_{i\in[k], \tilde{x}^i_\ell = j} \frac{\theta_i}{g} = b\lambda_j.
		\end{equation}
		Hence, Constraints (\ref{feasibility}) holds. Constraint (\ref{branchcoordinate}) also holds since $x^0_\ell$ is obviously $0$ and $x^1_\ell= \sum_{i\in [k]: \tilde{x}^i_\ell = 1}\frac{\theta_i}{g}= \lambda_1$. The rest of the constraints trivially hold. 
	\end{proof}
	This concludes the proof of Lemma \ref{LPClemma}.	
\end{proof}

We now show if $x'$ in the statement of Lemma \ref{LPClemma} is partially integral, we can find solutions with more integral components.
\begin{lemma}\label{round-up}
	Given $(x',y')\in \dom(P)$, such that $x'_1,\ldots,x'_{\ell-1}\in \{0,1\}$ for some $\ell\geq 1$, we can find in polynomial time vectors $(\hat{x}^0,\hat{y}^0),(\hat{x}^1,\hat{y}^1)$ and scalars $\gamma_0,\gamma_1 \in [0,1]$ such that: (i) $\frac{ 1}{g}\leq \gamma_0 + \gamma_1  \leq 1$, (ii) $(\hat{x}^0,\hat{y}^0)$ and $(\hat{x}^1,\hat{y}^1)$ are in  $\dom( P)$, (iii) $\hat{x}^0_\ell=0$ and $\hat{x}^1_\ell=1$, (iv) $ \gamma_0\hat{x}^0 +\gamma_1 \hat{x}^1 \leq
		x'$,(v) $\hat{x}^i_j\in \{0,1\}$ for $i=0,1$ and $j=1,\ldots,\ell-1$.
\end{lemma} 
\begin{proof}
	By Lemma \ref{LPClemma} we can find $(\bar{x}^0,\bar{y}^0)$, $(\bar{x}^1,\bar{y}^1)$, $\gamma_0$ and $\gamma_1$ that satisfy (i), (ii), (iii), and (iv). We define $\hat{x}^0$ and $\hat{x}^1$ as follows. For $i=0,1$, for $j=1,\ldots,\ell-1$, let $\hat{x}^i_j= \ceil{\bar{x}^i_j}$, for $j=\ell,\ldots,t$ let $\hat{x}^i_j = \bar{x}^i_j$.

	 We now show that $(\hat{x}^0,\bar{y}^0)$, $(\hat{x}^1,\bar{y}^1)$, $\gamma_0$, and $\gamma_1$ satisfy all the conditions. Note that conditions (i), (ii), (iii), and (v) are trivially satisfied. Thus we only need to show (iv) holds. We need to show that $\gamma_0 \hat{x}^0_j+\gamma_1\hat{x}^1_j\leq gx'_j$. If $j=\ell,\ldots,t$, then this clearly holds. Hence, assume $j\leq \ell-1$. By the property of $x'$ we have $x'_j\in \{0,1\}$. If $x'_j= 0$, then by Constraint (\ref{packing}) we have $\bar{x}^0_j = \bar{x}^1_j=0$. Therefore, $\hat{x}^i_j=0$ for $i=0,1$, so (iv) holds. Otherwise if $x'_j = 1$, then we have
	$\gamma_0\hat{x}^0_j+\gamma_1\hat{x}^1_j\leq \gamma_0+\gamma_1\leq 1\leq x'_j.$ 
	Therefore (v) holds.
\end{proof}

@@

	\begin{algorithm}[H]\label{FDTFull}
		\KwIn{$P= \{(x,y)\in \mathbb{R}^{n\times p}: Ax+Gy\geq b\}$ and $S=\{(x,y)\in P: x\in \{0,1\}^n\}$ such that $g=\max_{c\in \mathbb{R}^n_+ }\frac{\min_{(x,y)\in }cx}{\min_{(x,y)\in P}cx}$ is finite, $(x^*,y^*)\in P$}
		\KwOut{$(z^i,w^i)\in S$ and $\lambda_i\geq 0$ for $i=1,\ldots,k$ such that $\sum_{i=1}^{k}\lambda_i = 1$, and $\sum_{i=1}^{k}\lambda_iz^i\leq g^tx^*$ }
		$L^0\leftarrow [(x^*,y^*),1]$\\
		\For{$i=1$ \textbf{to} $t$}{
			$L'\leftarrow \emptyset$\\
			\For{$[(x,y),\lambda] \in L^i$}{
				Apply Lemma \ref{round-up} to obtain $[(\hat{x}^0,\hat{y}^0),\gamma_0]$ and $[(\hat{x}^1,\hat{y}^1),\gamma_1]$\\
				$L' \leftarrow L' \cup \{[(\hat{x}^0,\hat{y}^0),\lambda\cdot\gamma_0]\} \cup \{[(\hat{x}^1,\hat{y}^1),\lambda\cdot\gamma_1]\}$\\			
			}
			Apply Lemma \ref{prune} to $L'$ to obtain $L^{i+1}$. 
		}
		\For{$[(x,y),\lambda] \in L^t$}{
			Apply Algorithm \ref{domtoIPalg} to $(x,y)$ to obtain $(z,w)\in S$\\
			$F \leftarrow F \cup \{[(z,w),\lambda]\}$
		}
		\textbf{return} $F$
		\caption{Fractional Decomposition Tree Algorithm}
	\end{algorithm}
